Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-10-02 paper.tex
Clarify what x/D means

In order to visualize the mean velocity field, vector arrows for the mean
cross-stream and vertical components are superimposed on top of contours of the
streamwise component at $X/D=1$ in Figure~\ref{fig:br-cfd-mean-velocity}. Both
CFD models predict the general structure of the mean velocity well, though the
SA case has a slightly larger vertical mean flow component, which could be due
to stronger tip vortex generation, or lower diffusivity compared with the SST
model.

>>>>

In order to visualize the mean velocity field, vector arrows for the mean
cross-stream and vertical components are superimposed on top of contours of the
streamwise component at one rotor diameter downstream ($x/D=1$) of the axis in
Figure~\ref{fig:br-cfd-mean-velocity}. Both CFD models predict the general
structure of the mean velocity well, though the SA case has a slightly larger
vertical mean flow component, which could be due to stronger tip vortex
generation, or lower diffusivity compared with the SST model.
